Share Buyback and Equity Issue Anomalies Revisited

### 2016-04-17 bb_issuers_new.Rnw
new version - first commit. Files ending with "new" plus create_bbissuers_data.R

<< eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
#rm(list=ls()) # Clean up the memory, if we want to rerun from scratch
#dev.off();
#library(knitr); knit2pdf('bb_issuers.Rnw', texi2dvi='texi2dvi'); file.remove(paste("bb_issuers",c(".aux",".tex",".blg",".bbl",".log",".out"),sep=""))
#dir.create("tmpfiles") # need to comment this if the directory already exists

#load("tmpfiles/bb_issuersALL.Rdata")
reload_data = 0

# Then to make it into Word: 
# pandoc -s bb_issuers.tex --bibliography=bibliography.bib --number-sections --reference-links -o theo.docx

generate_all_data = 0 # set this to 1 if the data need to be re-generated from the csv's even though they already exist as .Rdata. 
# TIME ALIGNMENT IS KEY, SO WE HAVE A SEPARATE PART OF THE CODE FOR THIS
time_align_all_data = 0
# Some basic data generation that we need across events
rerun_buyback_data_code <- 0
rerun_issuers_data_code <- 0
# If we generate the cross-events data again
get_crossevent_data <- 0 # Old stuff, not used for now
# report_code is only customized to change the "high U-index" and "low U-index" companies, nothing else. Everything else is done in report_data.R
rerun_buyback_report_code <- 0
rerun_issuers_report_code <- 0
# All the RNW data
generate_rnw_data = 0

source("lib_helpers.R")
source("latex_code.R")
source("dataset/indices_and_factors/ff_industries_sic.R")
source("business_data_clean.R")
source("Paper_global_parameters.R")

if (generate_rnw_data == 1){
  source("bb_issuers.R")
}  else{
  if (reload_data)
    load("tmpfiles/bb_issuersALL.Rdata")
  source("lib_helpers.R") 
  source("latex_code.R")
  source("dataset/indices_and_factors/ff_industries_sic.R")
  source("business_data_clean.R")
  source("Paper_global_parameters.R")
}

@@

# use comma for 1000s
knit_hooks$set(inline = function(x) {
  if(is.numeric(x)){
    return(prettyNum(x, big.mark=","))
  }else{
    return(x)
  }
})

@@

\vspace{-.2in}
\begin{abstract}
\noindent We re-examine the behavior of stock returns after net issue announcements using the five-factor model proposed by Fama and French (2015a). We confirm their findings that the equity issue anomaly disappears with the five-factor model, but the buyback anomaly does not. Buyback announcements by firms with high pre-announcement (idiosyncratic) volatility are followed by higher long-term abnormal returns. This is inconsistent with the widely documented low volatility anomaly, but consistent with Stambaugh, Yu, and Yuan (2015) who find a positive relation between stock returns and idiosyncratic volatility for undervalued stocks.

\end{abstract}
\vspace{2cm}

@@

@@

For the buybacks we combined all open market repurchase announcements from both the SDC Repurchases data base and the SDC US mergers and acquisitions ($M\&A$) data base.\footnote{More information is available upon request. An interactive online tool to explore data variations and robustness analyses of all results in this paper, as well as all the source code, is also available upon request.}   We ended up with a total of \Sexpr{cleanup_bb$Standardise$final_merge_data} repurchases events, out of which \Sexpr{cleanup_bb$Standardise$only_repurchase_deals} were only from the SDC Repurchases database, \Sexpr{cleanup_bb$Standardise$only_MA_deals} only from the SDC $M\&A$ database and \Sexpr{cleanup_bb$Standardise$overlap_deals} from both. Finally, we removed the following events: no CRSP returns available (\Sexpr{cleanup_bb$get_crsp$NOPERMNO_remove + cleanup_bb$merge$CRSP_remove} events); not all Compustat data available (\Sexpr{cleanup_bb$compustat$NO_GVKEY_remove + cleanup_bb$merge$compustat_remove} events); the percent of shares authorized was larger than \Sexpr{MAX_EVENT_SIZE}$\%$ (\Sexpr{cleanup_bb$biz_clean$EventSize_filter} events), or the closing price was less than \$\Sexpr{penny_stock_price_old} for events before 1995 or \$\Sexpr{penny_stock_price_recent} for the other (\Sexpr{cleanup_bb$biz_clean$Penny_stock_filter} events), or  the primary stock exchange was not the NYSE, the Nasdaq, or Amex (\Sexpr{cleanup_bb$biz_clean$major_markets_only} events).  Finally, we removed all events from firms in the Financial and Utilities sectors (\Sexpr{length(BUYBACK_DATA$finance_Size_used)}  events).\footnote{We are using the industries from Kenneth French's Website. The Financial Sector consists of all firms with SIC code at the time of the buyback announcement that belonged in the ``Banks'' or ``Fin'' industries (SIC codes 6000 to 6300 and 6700 to 6799). The Utilities Sector consists of all firms with SIC code 4900 to 4942.}  At the end we are left with \Sexpr{length(cusip_bb)} buyback events made by \Sexpr{length(unique(cusip_bb))} firms. The average percent of shares authorized for these firms was \Sexpr{datasummaryBB["Percent authorized", "Mean"]}$\%$ (median of \Sexpr{datasummaryBB["Percent authorized", "Median"]}$\%$), the average Market Capitalization at announcement was \$\Sexpr{datasummaryBB["Market cap.", "Mean"]} Million (median of \$\Sexpr{datasummaryBB["Market cap.", "Median"]} Million), while the BE/ME was on average \Sexpr{datasummaryBB["BE/ME", "Mean"]} (median of \Sexpr{datasummaryBB["BE/ME", "Median"]}).

For the issuers, we started with \Sexpr{cleanup_iss$Standardise$SDC_initial_data} events from SDC, filtered to exclude rights issues, pure secondary offerings where existing shareholders sell shares without generating proceeds for the company,  issues made by non-U.S. firms or in non-U.S. markets, issues made by closed-end funds or unit investment trusts, as well as block trades, accelerated offers and best efforts. We removed all SDC events for which either the event date (\Sexpr{cleanup_iss$Standardise$SDC_NODATE} events) or the CUSIP (\Sexpr{cleanup_iss$Standardise$SDC_NOCUSIP} events) was missing or where we found duplicate events with mismatching information (\Sexpr{cleanup_iss$Standardise$BAD_DUPLICATES} events), a total of \Sexpr{cleanup_iss$Standardise$SDC_standardize_removal} events - given the overlap between these cases. Finally, as for the buybacks, we removed the following events: no CRSP returns available (\Sexpr{cleanup_iss$get_crsp$NOPERMNO_remove + cleanup_iss$merge$CRSP_remove} events); not all Compustat data available (\Sexpr{cleanup_iss$compustat$NO_GVKEY_remove + cleanup_iss$merge$compustat_remove} events); the percent of shares authorized was larger than \Sexpr{MAX_EVENT_SIZE}$\%$ (\Sexpr{cleanup_iss$biz_clean$EventSize_filter} events), or the closing price was less than \$\Sexpr{penny_stock_price_old} for events before 1995 or \$\Sexpr{penny_stock_price_recent} for the other (\Sexpr{cleanup_iss$biz_clean$Penny_stock_filter} events), or  the stocks were not listed on the NYSE, Nasdaq or Amex (\Sexpr{cleanup_iss$biz_clean$major_markets_only} events). We again removed all events from firms in the Financial and Utilities sectors (\Sexpr{length(ISSUERS_DATA$finance_Size_used)} events). Our final sample contains \Sexpr{length(cusip_iss)} events made by \Sexpr{length(unique(cusip_iss))} firms. The average percent of shares issued was \Sexpr{datasummaryISS["Percent authorized", "Mean"]}$\%$ (median of \Sexpr{datasummaryISS["Percent authorized", "Median"]}$\%$), the average Market Capitalization on the announcement day  was \$\Sexpr{datasummaryISS["Market cap.", "Mean"]} Million (median of \$\Sexpr{datasummaryISS["Market cap.", "Median"]} Million), while the BE/ME was on average \Sexpr{datasummaryISS["BE/ME", "Mean"]} (median of \Sexpr{datasummaryISS["BE/ME", "Median"]}).

@@

Table~\ref{tbl:PastFindingsTimeBB} shows excess returns, using both the IRATS and Calendar Time method for different time periods. We consider time periods, which overlap to some extent with past research [\cite{IkenberryLakonishokVermaelen1995}; \cite{PeyerVermaelen2009}; \cite{ManconiPeyerVermaelen2015}; and \cite{FuHuang2015}]: 1985-1990; 1991-2000; 2001-2014 and 2008-2014. The last period was chosen to incorporate the financial crisis and to test whether indeed markets have become more efficient in recent years, or whether managers have for example been discouraged from market timing by the obvious mistakes that were made by buying back shares before a major financial crisis.

Table~\ref{tbl:PastFindingsTimeBB} shows that, regardless of the time period chosen or the method to calculate excess returns, the buyback anomaly remains economically and statistically significant and there is no clear time trend in the data that suggests that markets have become more efficient over time. For example, although the 2001-2014 period shows smaller timing ability than the 1990-2000 period, excess returns in the 2008-2014 period are as large as in the 1991-2000 period: approximately \Sexpr{BBtable_time["+48",22]}$\%$  after 4 years using IRATS or \Sexpr{BBtable_time_cal["+48",22]}$\%$ per month (\Sexpr{48*BBtable_time_cal["+48",22]}$\%$ after 4 years) when we use the Calendar Time method. There is one exception to the consistency between the IRATS and the Calendar Time results: in the period of 1991-2000, the IRATS method generates excess returns after 48 months of \Sexpr{BBtable_time["+48",10]}$\%$ (t=\Sexpr{BBtable_time["+48",11]}) but the Calendar Time method produces statistically insignificant excess returns of \Sexpr{BBtable_time_cal["+48",10]}$\%$ per month. This result appears to also be inconsistent with \cite{PeyerVermaelen2009}. However, if one includes the financial sector firms or considers the three-factor model, as \cite{PeyerVermaelen2009} do, the calendar method abnormal returns do become significant.\footnote{Details available upon request.}

Table~\ref{tbl:PastFindingsTimeUnderBB} re-examines whether the U-index of \cite{PeyerVermaelen2009} predicts the five factor excess returns for different time periods. The first two columns show the IRATS results and the last two columns show the Calendar Time results. Regardless of the method to compute excess returns, the U-index is an excellent predictor: except for the very short 1985-1990 period, buybacks announced by high U-index firms are followed by significantly larger returns than buybacks announced by low U-index firms.  There is also no evidence that the U-index is losing its predictive power over time: for example, in the 2001-2014 period the difference between high and low U-index firms (after 48 months, IRATS) was \Sexpr{BBtable_undertime["+48",31]-BBtable_undertime["+48",34]}$\%$, while in the most recent 2008-2014 period high U-index firms had \Sexpr{BBtable_undertime["+48",43]-BBtable_undertime["+48",46]}$\%$ larger abnormal returns than low U-index firms.

@@

For each event we measure their pre-announce returns volatility with the standard deviation of their daily stock returns over the 6 months prior to the buyback announcement. We define two types of events: ``low volatility'' and ``high volatility'' events, depending on whether volatility was in the top or bottom \Sexpr{round(100*quantile_VOL,2)}$\%$ of the volatilities of all CRSP companies, as we did for $R^2$ above:
each month we use the daily returns of all CRSP stocks for the previous 6 months until the one before last day of the previous month to calculate all companies' daily returns volatilities. We also define the volatility score of a firm to be the percentile of its volatility across all CRSP firms that month. Note that, again, we do not need to  define 20 breakpoints as Fama-French do, and for simplicity we focus on the two extreme quantiles only.  In total we have \Sexpr{length(High_VOL_eventsBB)} ``high volatility'' buybacks-events and \Sexpr{length(Low_VOL_eventsBB)} ``low volatility'' ones. Table~\ref{tbl:industriesR2Vol}, columns (3) and (4)  show the percentage of high and low volatility events across all industries for which we have at least 100 buyback events in our sample.

@@

<<  eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
EU_index_features = scrub(cbind(BUYBACK_DATA$DATASET$SDC$minus_Rsq_returns, BUYBACK_DATA$DATASET$SDC$pre_vol,BUYBACK_DATA$Valuation_Index))
colnames(EU_index_features) <- c("Idiosyncratic Score", "Volatility Score", "U-Index Score")
Under_IdioBB_cor = cor(EU_index_features)
@

@@

<<   eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
printLatexTable2(
  cbind(IRATS_table_all_bb,IRATS_table_all_bb_undervaluation)[reported_times,],
  cbind(CAL_table_all_bb,CAL_table_all_bb_undervaluation)[reported_times,],
  columns = c("All 3F","All 5F","High U-index 3F","Low U-index 3F","High U-index 5F","Low U-index 5F"),
  title="Buyback announcements during 1985-2014",
  title1 = "Panel A: IRATs Cumulative Abnormal Returns",
  title2 = "Panel B: Calendar Time Method Monthly Abnormal Returns",
  caption="The table presents the abnormal returns for firms after open market repurchase announcements from the announcement date until $t$ months after announcement. We include a version of the abnormal returns for the full sample and one for both companies with a high U-index and a low U-index. Panel~A reports monthly cumulative average abnormal returns (CAR) in percent using \\cite{ibbotson1975} returns across time and security (IRATS) method combined with the \\cite{FamaFrench1993} three-factor model and the \\cite{FamaFrench2015a} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples. The following regressions are run each event month~$j$:\\vspace{-1em}
\\begin{eqnarray*}
(R_{i,t} - R_{f,t}) &=& a_j + b_j (R_{m,t} - R_{f,t}) + c_j {SMB}_t + d_j {HML}_t + \\epsilon_{i,t}, \\\\
(R_{i,t} - R_{f,t}) &=& a_j + b_j (R_{m,t} - R_{f,t}) + c_j {SMB}_t + d_j {HML}_t + e_t {RMW}_t + f_t {CMA}_t + \\epsilon_{i,t},
\\end{eqnarray*}
where $R_{i,t}$ is the monthly return on security $i$ in the calendar month $t$ that corresponds to the event month $j$, with $j = 0$ being the month of the repurchase announcement. $R_{f,t}$ and $R_{m,t}$ are the risk-free rate and the return on the equally weighted CRSP index, respectively. ${SMB}_t$, ${HML_t}$, ${RMW}_t$, ${CMA}_t$ are the monthly returns on the size, book-to-market factor, profitability factor and investment factor in month $t$, respectively. The numbers reported are sums of the intercepts of cross-sectional regressions over the relevant event-time-periods expressed in percentage terms. The standard error (denominator of the $t$-statistic) for a window is the square root of the sum of the squares of the monthly standard errors. Panel~B reports monthly average abnormal returns (AR) of equally weighted Calendar Time portfolios using the \\cite{FamaFrench2015a} five-factor model. In this method, event firms that have announced an open market buyback in the last calendar months form the basis of the calendar month portfolio. A single time-series regression is run with the excess returns of the calendar portfolio as the dependent variable and the returns of five factors as the independent variables. The significance levels are indicated by * and ** and correspond to a significance level of $5\\%$ and $1\\%$ respectively, using a two-tailed test.
",
label = "tbl:priorBuybacks",
bigtitleontop=T,
titleontop=T,
metric1 = "CAR",
metric2 = "AR",
scale=1,
lastSpecial=T,
dorotate=T
)

@@

<<  eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
printLatexTable2(
  Exit_on_SEO_Abn_table[reported_times,],
  Exit_on_SEO_Abn_table_cal[reported_times,],
  columns = c("No Issue","Issue"),
  title="Buybacks with and without subsequent issue",
  title1 = "Panel A: IRATs Cumulative Abnormal Returns",
  title2 = "Panel B: Calendar Method Monthly Abnormal Returns",
  caption="The table presents the long-run abnormal returns for firms repurchase announcements for events with and without a subsequent SEO announcement. Panel~A reports monthly cumulative average abnormal returns (CAR) in percent using \\cite{ibbotson1975} returns across time and security (IRATS) method combined with the \\cite{FamaFrench2015a} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples. The following regression is run each event month~$j$:
\\begin{eqnarray*}
(R_{i,t} - R_{f,t}) &=& a_j + b_j (R_{m,t} - R_{f,t}) + c_j {SMB}_t + d_j {HML}_t + e_t {RMW}_t + f_t {CMA}_t + \\epsilon_{i,t},
\\end{eqnarray*}
where $R_{i,t}$ is the monthly return on security $i$ in the calendar month $t$ that corresponds to the event month $j$, with $j = 0$ being the month of the repurchase announcement. $R_{f,t}$ and $R_{m,t}$ are the risk-free rate and the return on the equally weighted CRSP index, respectively. ${SMB}_t$, ${HML_t}$, ${RMW}_t$, ${CMA}_t$ are the monthly returns on the size, book-to-market factor, profitability factor and investment factor in month $t$, respectively. The numbers reported are sums of the intercepts of cross-sectional regressions over the relevant event-time-periods expressed in percentage terms. The standard error (denominator of the $t$-statistic) for a window is the square root of the sum of the squares of the monthly standard errors. Panel~B reports monthly average abnormal returns (AR) of equally weighted Calendar Time portfolios using the \\cite{FamaFrench2015a} five-factor model. In this method, event firms that have announced an open market buyback in the last calendar months form the basis of the calendar month portfolio. A single time-series regression is run with the excess returns of the calendar portfolio as the dependent variable and the returns of five factors as the independent variables. The significance levels are indicated by * and ** and correspond to a significance level of $5\\%$ and $1\\%$ respectively, using a two-tailed test.",

>>>>

<< eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
#dev.off();
#library(knitr); knit2pdf('bb_issuers_new.Rnw', texi2dvi='texi2dvi'); file.remove(paste("bb_issuers_new",c(".aux",".tex",".blg",".bbl",".log",".out"),sep=""))
#dir.create("tmpfiles") # need to comment this if the directory already exists
# Then to make it into Word: 
# pandoc -s bb_issuers_new.tex --bibliography=bibliography.bib --number-sections --reference-links -o theo.docx

rm(list=ls()) # Clean up the memory, if we want to rerun from scratch

generate_all_data = 0 # set this to 1 if the data need to be re-generated from scratch
generate_rnw_data = 0 # set this to 1 to generate the .Rnw data

if (generate_all_data == 1){
  source("create_bbissuers_data.R")
}
if (generate_rnw_data == 1){
  source("bb_issuers_new.R")
} else {
  load("bb_issuers_new.Rdata")
}

source("../FinanceLibraries/lib_helpers.R")
source("../FinanceLibraries/latex_code.R")
source("../FinanceData/rawdata_fama_french/ff_industries_sic.R")
source("Paper_global_parameters.R")

@@

inline_hook <- function (x) {
  if (is.numeric(x)) {
    # ifelse does a vectorized comparison
    # If integer, print without decimal; otherwise print two places
    res <- ifelse(x == round(x),
                  # use comma for 1000s
                  sprintf("%s", prettyNum(x, big.mark=",")),
                  sprintf("%.2f", x)
    )
    paste(res, collapse = ", ")
  } else {
    x
  }
}
knit_hooks$set(inline = inline_hook)
@

@@

\vspace{-.2in}
\begin{abstract}
\noindent  We find that, inconsistent with the well-known low volatility anomaly, post-buyback announcement long-term abnormal returns are higher when the pre-announcement (idiosyncratic) volatility is high, and not significant otherwise. This is consistent with \cite{Stambaugh2015} who find a positive relation between stock returns and idiosyncratic volatility for undervalued stocks. The results hold for both small and large firms. We also find no post-equity issue abnormal returns when using the five-factor model proposed by Fama and French (2015a). However, the post-buyback announcement abnormal returns are also higher for firms that subsequently announce an equity issue. Finally, based on our findings we extend the Undervaluation Index of \citep{PeyerVermaelen2009}.  
\end{abstract}
\vspace{2cm}

@@

<< fig.width=10, fig.height=6, out.width='\\textwidth', echo=F >>=
cleanup_bb = list()
cleanup_bb$Standardise <- BUYBACK_DATA$cleanupSDC$Standardise
cleanup_bb$biz_clean <- BUYBACK_DATA$cleanupBIZ
cusip_bb = BUYBACK_DATA$DATASET$SDC$CUSIP
event.date_bb = BUYBACK_DATA$DATASET$SDC$Event.Date
permno_bb = BUYBACK_DATA$DATASET$SDC$permno

cleanup_iss = list()
cleanup_iss$Standardise <- ISSUERS_DATA$cleanupSDC$Standardise
cleanup_iss$biz_clean <- ISSUERS_DATA$cleanupBIZ
cusip_iss = ISSUERS_DATA$DATASET$SDC$CUSIP
event.date_iss = ISSUERS_DATA$DATASET$SDC$Event.Date
permno_iss = ISSUERS_DATA$DATASET$SDC$permno
@

@@

For the buybacks we combined all open market repurchase announcements from both the SDC Repurchases data base and the SDC US mergers and acquisitions ($M\&A$) data base.\footnote{More information is available upon request. An interactive online tool to explore data variations and robustness analyses of all results in this paper, as well as all the source code, is also available upon request.}   We ended up with a total of \Sexpr{cleanup_bb$Standardise$final_merge_data} repurchases events, out of which \Sexpr{cleanup_bb$Standardise$only_repurchase_deals} were only from the SDC Repurchases database, \Sexpr{cleanup_bb$Standardise$only_MA_deals} only from the SDC $M\&A$ database and \Sexpr{cleanup_bb$Standardise$overlap_deals} from both. Finally, we removed the following events: no CRSP returns or not all Compustat data available (\Sexpr{BUYBACK_DATA$cleanupNoPermno +  BUYBACK_DATA$cleanupNoCRSPdata + BUYBACK_DATA$cleanupMissingSomeValues} events); the percent of shares authorized was larger than \Sexpr{MAX_EVENT_SIZE}$\%$ (\Sexpr{cleanup_bb$biz_clean$EventSize_filter} events), or the closing price was less than \$\Sexpr{penny_stock_price_old} for events before 1995 or \$\Sexpr{penny_stock_price_recent} for the other (\Sexpr{cleanup_bb$biz_clean$Penny_stock_filter} events), or  the primary stock exchange was not the NYSE, the Nasdaq, or Amex (\Sexpr{cleanup_bb$biz_clean$major_markets_only} events).  Finally, we removed all events from firms in the Financial and Utilities sectors (\Sexpr{sum(BUYBACK_DATA$cleanupBIZ$Industry_filter)}  events).\footnote{We are using the industries from Kenneth French's Website. The Financial Sector consists of all firms with SIC code at the time of the buyback announcement that belonged in the ``Banks'' or ``Fin'' industries (SIC codes 6000 to 6300 and 6700 to 6799). The Utilities Sector consists of all firms with SIC code 4900 to 4942.}  At the end we are left with \Sexpr{length(cusip_bb)} buyback events made by \Sexpr{length(unique(cusip_bb))} firms. The average percent of shares authorized for these firms was \Sexpr{datasummaryBB["Percent authorized", "Mean"]}$\%$ (median of \Sexpr{datasummaryBB["Percent authorized", "Median"]}$\%$), the average Market Capitalization at announcement was \$\Sexpr{datasummaryBB["Market cap.", "Mean"]} Million (median of \$\Sexpr{datasummaryBB["Market cap.", "Median"]} Million), while the BE/ME was on average \Sexpr{datasummaryBB["BE/ME", "Mean"]} (median of \Sexpr{datasummaryBB["BE/ME", "Median"]}).

For the issuers, we started with \Sexpr{cleanup_iss$Standardise$SDC_initial_data} events from SDC, filtered to exclude rights issues, pure secondary offerings where existing shareholders sell shares without generating proceeds for the company,  issues made by non-U.S. firms or in non-U.S. markets, issues made by closed-end funds or unit investment trusts, as well as block trades, accelerated offers and best efforts. We removed all SDC events for which either the event date (\Sexpr{cleanup_iss$Standardise$SDC_NODATE} events) or the CUSIP (\Sexpr{cleanup_iss$Standardise$SDC_NOCUSIP} events) was missing or where we found duplicate events with mismatching information (\Sexpr{cleanup_iss$Standardise$BAD_DUPLICATES} events), a total of \Sexpr{cleanup_iss$Standardise$SDC_standardize_removal} events - given the overlap between these cases. Finally, as for the buybacks, we removed the following events: no CRSP returns or not all Compustat data available (\Sexpr{ISSUERS_DATA$cleanupNoPermno +  ISSUERS_DATA$cleanupNoCRSPdata + ISSUERS_DATA$cleanupMissingSomeValues} events); the percent of shares authorized was larger than \Sexpr{MAX_EVENT_SIZE}$\%$ (\Sexpr{cleanup_iss$biz_clean$EventSize_filter} events), or the closing price was less than \$\Sexpr{penny_stock_price_old} for events before 1995 or \$\Sexpr{penny_stock_price_recent} for the other (\Sexpr{cleanup_iss$biz_clean$Penny_stock_filter} events), or  the stocks were not listed on the NYSE, Nasdaq or Amex (\Sexpr{cleanup_iss$biz_clean$major_markets_only} events). We again removed all events from firms in the Financial and Utilities sectors (\Sexpr{sum(ISSUERS_DATA$cleanupBIZ$Industry_filter)} events). Our final sample contains \Sexpr{length(cusip_iss)} events made by \Sexpr{length(unique(cusip_iss))} firms. The average percent of shares issued was \Sexpr{datasummaryISS["Percent authorized", "Mean"]}$\%$ (median of \Sexpr{datasummaryISS["Percent authorized", "Median"]}$\%$), the average Market Capitalization on the announcement day  was \$\Sexpr{datasummaryISS["Market cap.", "Mean"]} Million (median of \$\Sexpr{datasummaryISS["Market cap.", "Median"]} Million), while the BE/ME was on average \Sexpr{datasummaryISS["BE/ME", "Mean"]} (median of \Sexpr{datasummaryISS["BE/ME", "Median"]}).

@@

Table~\ref{tbl:PastFindingsTimeBB} shows excess returns, using both the IRATS and Calendar Time method for different time periods. We consider time periods, which overlap to some extent with past research [\cite{IkenberryLakonishokVermaelen1995}; \cite{PeyerVermaelen2009}; \cite{ManconiPeyerVermaelen2015}; and \cite{FuHuang2015}]: 1985-1990; 1991-2000; 2001-2015 and 2008-2015. The last period was chosen to incorporate the financial crisis and to test whether indeed markets have become more efficient in recent years, or whether managers have for example been discouraged from market timing by the obvious mistakes that were made by buying back shares before a major financial crisis.

Table~\ref{tbl:PastFindingsTimeBB} shows that, regardless of the time period chosen or the method to calculate excess returns, the buyback anomaly remains economically and statistically significant and there is no clear time trend in the data that suggests that markets have become more efficient over time. For example, although the 2001-2015 period shows smaller timing ability than the 1990-2000 period, excess returns in the 2008-2015 period are as large as in the 1991-2000 period: approximately \Sexpr{BBtable_time["+48",22]}$\%$  after 4 years using IRATS or \Sexpr{BBtable_time_cal["+48",22]}$\%$ per month (\Sexpr{48*BBtable_time_cal["+48",22]}$\%$ after 4 years) when we use the Calendar Time method. There is one exception to the consistency between the IRATS and the Calendar Time results: in the period of 1991-2000, the IRATS method generates excess returns after 48 months of \Sexpr{BBtable_time["+48",10]}$\%$ (t=\Sexpr{BBtable_time["+48",11]}) but the Calendar Time method produces statistically insignificant excess returns of \Sexpr{BBtable_time_cal["+48",10]}$\%$ per month. This result appears to also be inconsistent with \cite{PeyerVermaelen2009}. However, if one includes the financial sector firms or considers the three-factor model, as \cite{PeyerVermaelen2009} do, the calendar method abnormal returns do become significant.\footnote{Details available upon request.}

Table~\ref{tbl:PastFindingsTimeUnderBB} re-examines whether the U-index of \cite{PeyerVermaelen2009} predicts the five factor excess returns for different time periods. The first two columns show the IRATS results and the last two columns show the Calendar Time results. Regardless of the method to compute excess returns, the U-index is an excellent predictor: except for the very short 1985-1990 period, buybacks announced by high U-index firms are followed by significantly larger returns than buybacks announced by low U-index firms.  There is also no evidence that the U-index is losing its predictive power over time: for example, in the 2001-2015 period the difference between high and low U-index firms (after 48 months, IRATS) was \Sexpr{BBtable_undertime["+48",31]-BBtable_undertime["+48",34]}$\%$, while in the most recent 2008-2015 period high U-index firms had \Sexpr{BBtable_undertime["+48",43]-BBtable_undertime["+48",46]}$\%$ larger abnormal returns than low U-index firms.

@@

For each event we measure their pre-announce returns volatility with the standard deviation of their daily stock returns over the 6 months prior to the buyback announcement. We define two types of events: ``low volatility'' and ``high volatility'' events, depending on whether volatility was in the top or bottom \Sexpr{round(100*quantile_VOL,2)}$\%$ of the volatilities of all CRSP companies, as we did for $R^2$ above:
each month we use the daily returns of all CRSP stocks for the previous 6 months until the one before last day of the previous month to calculate all companies' daily returns volatilities. We also define the volatility score of a firm to be the percentile of its volatility across all CRSP firms that month. Note that, again, we do not need to  define 20 breakpoints as Fama-French do, and for simplicity we focus on the two extreme quantiles only.  In total we have \Sexpr{sum(High_VOL_eventsBB)} ``high volatility'' buybacks-events and \Sexpr{sum(Low_VOL_eventsBB)} ``low volatility'' ones. Table~\ref{tbl:industriesR2Vol}, columns (3) and (4)  show the percentage of high and low volatility events across all industries for which we have at least 100 buyback events in our sample.

@@

<<  eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
#EU_index_features = scrub(cbind(BUYBACK_DATA$DATASET$SDC$minus_Rsq_returns, BUYBACK_DATA$DATASET$SDC$pre_vol,BUYBACK_DATA$Valuation_Index))
#colnames(EU_index_features) <- c("Idiosyncratic Score", "Volatility Score", "U-Index Score")
#Under_IdioBB_cor = cor(EU_index_features)
@

@@

<<   eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
printLatexTable2(
  cbind(IRATS_table_all_bb,IRATS_table_all_bb_undervaluation)[reported_times,],
  cbind(CAL_table_all_bb,CAL_table_all_bb_undervaluation)[reported_times,],
  columns = c("All 3F","All 5F","High U-index 3F","Low U-index 3F","High U-index 5F","Low U-index 5F"),
  title="Buyback announcements during 1985-2015",
  title1 = "Panel A: IRATs Cumulative Abnormal Returns",
  title2 = "Panel B: Calendar Time Method Monthly Abnormal Returns",
  caption="The table presents the abnormal returns for firms after open market repurchase announcements from the announcement date until $t$ months after announcement. We include a version of the abnormal returns for the full sample and one for both companies with a high U-index and a low U-index. Panel~A reports monthly cumulative average abnormal returns (CAR) in percent using \\cite{ibbotson1975} returns across time and security (IRATS) method combined with the \\cite{FamaFrench1993} three-factor model and the \\cite{FamaFrench2015a} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples. The following regressions are run each event month~$j$:\\vspace{-1em}
\\begin{eqnarray*}
(R_{i,t} - R_{f,t}) &=& a_j + b_j (R_{m,t} - R_{f,t}) + c_j {SMB}_t + d_j {HML}_t + \\epsilon_{i,t}, \\\\
(R_{i,t} - R_{f,t}) &=& a_j + b_j (R_{m,t} - R_{f,t}) + c_j {SMB}_t + d_j {HML}_t + e_t {RMW}_t + f_t {CMA}_t + \\epsilon_{i,t},
\\end{eqnarray*}
where $R_{i,t}$ is the monthly return on security $i$ in the calendar month $t$ that corresponds to the event month $j$, with $j = 0$ being the month of the repurchase announcement. $R_{f,t}$ and $R_{m,t}$ are the risk-free rate and the return on the equally weighted CRSP index, respectively. ${SMB}_t$, ${HML_t}$, ${RMW}_t$, ${CMA}_t$ are the monthly returns on the size, book-to-market factor, profitability factor and investment factor in month $t$, respectively. The numbers reported are sums of the intercepts of cross-sectional regressions over the relevant event-time-periods expressed in percentage terms. The standard error (denominator of the $t$-statistic) for a window is the square root of the sum of the squares of the monthly standard errors. Panel~B reports monthly average abnormal returns (AR) of equally weighted Calendar Time portfolios using the \\cite{FamaFrench2015a} five-factor model. In this method, event firms that have announced an open market buyback in the last calendar months form the basis of the calendar month portfolio. A single time-series regression is run with the excess returns of the calendar portfolio as the dependent variable and the returns of five factors as the independent variables. The significance levels are indicated by +, *, and ** and correspond to a significance level of $10\\%$, $5\\%$, and $1\\%$ respectively, using a two-tailed test.
",
label = "tbl:priorBuybacks",
bigtitleontop=T,
titleontop=T,
metric1 = "CAR",
metric2 = "AR",
scale=1,
lastSpecial=T,
dorotate=T
)

@@

<<  eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
printLatexTable2(
  Exit_on_SEO_Abn_table[reported_times,],
  Exit_on_SEO_Abn_table_cal[reported_times,],
  columns = c("No Issue","Issue"),
  title="Buybacks with and without subsequent issue",
  title1 = "Panel A: IRATs Cumulative Abnormal Returns",
  title2 = "Panel B: Calendar Method Monthly Abnormal Returns",
  caption="The table presents the long-run abnormal returns for firms repurchase announcements for events with and without a subsequent SEO announcement. Panel~A reports monthly cumulative average abnormal returns (CAR) in percent using \\cite{ibbotson1975} returns across time and security (IRATS) method combined with the \\cite{FamaFrench2015a} five-factor model for the sample of firms that announced an open market share repurchase plus various subsamples. The following regression is run each event month~$j$:
\\begin{eqnarray*}
(R_{i,t} - R_{f,t}) &=& a_j + b_j (R_{m,t} - R_{f,t}) + c_j {SMB}_t + d_j {HML}_t + e_t {RMW}_t + f_t {CMA}_t + \\epsilon_{i,t},
\\end{eqnarray*}
where $R_{i,t}$ is the monthly return on security $i$ in the calendar month $t$ that corresponds to the event month $j$, with $j = 0$ being the month of the repurchase announcement. $R_{f,t}$ and $R_{m,t}$ are the risk-free rate and the return on the equally weighted CRSP index, respectively. ${SMB}_t$, ${HML_t}$, ${RMW}_t$, ${CMA}_t$ are the monthly returns on the size, book-to-market factor, profitability factor and investment factor in month $t$, respectively. The numbers reported are sums of the intercepts of cross-sectional regressions over the relevant event-time-periods expressed in percentage terms. The standard error (denominator of the $t$-statistic) for a window is the square root of the sum of the squares of the monthly standard errors. Panel~B reports monthly average abnormal returns (AR) of equally weighted Calendar Time portfolios using the \\cite{FamaFrench2015a} five-factor model. In this method, event firms that have announced an open market buyback in the last calendar months form the basis of the calendar month portfolio. A single time-series regression is run with the excess returns of the calendar portfolio as the dependent variable and the returns of five factors as the independent variables. The significance levels are indicated by +, *, and ** and correspond to a significance level of $10\\%$, $5\\%$, and $1\\%$ respectively, using a two-tailed test.",
